\documentclass[letterpaper,10pt]{article}
\usepackage[T1]{fontenc}
\usepackage{mathpazo}
\usepackage{microtype} % better line-breaking, fewer overfull boxes / short lines
\usepackage{multicol}
\usepackage{tabularx}
\setlength{\multicolsep}{0pt}
\usepackage{enumitem}

\usepackage{contour}
\usepackage{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\pagestyle{empty}

\usepackage{geometry}
\geometry{left=0.6in, right=0.6in, top=0.6in, bottom=0.6in}
% Tighten lists globally to avoid manual parskip adjustments
\setlist{topsep=1pt, itemsep=1pt, parsep=1pt, partopsep=0pt}

\usepackage{titlesec}
% Section headers: bold caps + a thin rule underneath for scanability
\titleformat{\subsection}{\normalfont\large\bfseries}{}{0em}{}[{\vspace{1pt}\titlerule[0.6pt]}]
\titlespacing{\subsection}{0pt}{5pt}{3pt}
\titlespacing{\subsubsection}{0pt}{6pt}{0pt}

% House-style annotation sub-line (used under an entry's title line everywhere)
\newcommand{\subnote}[1]{{\small\itshape #1}}

% Right-margin year marker for the first entry of each year in the publication list.
% Zero-width box, so it adds no horizontal/vertical space -- the year floats into the
% right margin beside the entry's first line, giving a scannable year rail.
\newcommand{\yr}[1]{\makebox[0pt][l]{\hspace{\linewidth}\hspace{5pt}\small\bfseries #1}\ignorespaces}

% Journal / venue name style in the publication list. Bold mixed-case: strong salience
% while staying readable and preserving intentional casing (eBioMedicine, npj). To try
% another look, change only this line (e.g. {\textsc{#1}} for small-caps).
\newcommand{\journal}[1]{\textbf{#1}}

% Last-resort stretch to absorb long unbreakable strings (URLs) and kill overfull boxes
\setlength{\emergencystretch}{2em}

% Ragged (non-justified) X column for the reviewer table, prevents overfull cells
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

\usepackage[hidelinks]{hyperref}

% --- PACKAGES FOR AUTOMATION ---
\usepackage{totcount} % To count total number of publications
\usepackage[yyyymmdd]{datetime} % To format the date as YYYY-MM-DD

% --- AUTOMATION COMMANDS ---
\regtotcounter{enumi} % Register the 'enumerate' counter for total counting
\newcommand{\CVDate}{2026-07-03}

% For counting first-author papers
\newcounter{firstauthorcount}
\regtotcounter{firstauthorcount}
\newcommand{\faitem}{\refstepcounter{firstauthorcount}\item}

% --- GOOGLE SCHOLAR METRICS (manually generated) ---
\input{scholar_metrics.tex}

\begin{document}
\par{
      \centering{\textbf{\LARGE Haogao \textsc{Gu}}}\bigskip

      722 W 168th St, \hfill E-mail: \texttt{work@guhaogao.com}\\
      New York, NY 10032 \hfill Website: \href{https://guhaogao.com}{guhaogao.com}

      \setlength{\parskip}{-8pt}\hrulefill
}

\subsection*{EDUCATION}
\begin{itemize}
      \item \textbf{PhD} (\textit{Infectious Disease}), \textbf{The University of Hong Kong} \hfill Sep. 2016 -- Oct. 2020
      \item \textbf{BMed} (\textit{Preventive Medicine}), \textbf{Sun Yat-sen University}  \hfill Sep. 2011 -- Jun. 2016
\end{itemize}

%% -------------- Research Experience
\subsection*{EXPERIENCE}
\begin{itemize}

      \item \textbf{Associate Research Scientist} (\textit{Mailman School of Public Health}), \textbf{Columbia University} \hfill Jun. 2026 -- Present \\ \small \textit{PI: Sen Pei, Department of Environmental Health Sciences} \normalsize
      \item \textbf{Research Assistant Professor} (\textit{School of Public Health}), \textbf{The University of Hong Kong} \hfill Jul. 2024 -- Jun. 2026
      \item \textbf{Visiting Scholar} (\textit{Evolutionary dynamics of infectious diseases}), \textbf{Institut Pasteur} \hfill Dec. 2024 -- Feb. 2025 \\ \small \textit{Host: Sebastian Duchene, Department of Computational Biology} \normalsize
      \item \textbf{Postdoctoral Fellow} (\textit{School of Public Health}), \textbf{The University of Hong Kong} \hfill Jan. 2021 -- Jun. 2024 \\	\small \textit{Mentor: Leo Poon, Department of Laboratory Sciences} \normalsize

\end{itemize}

\subsection*{HONORS AND AWARDS}
\begin{itemize}
      \item \textbf{Gold Medal}, 51st International Exhibition of Inventions at Geneva \hfill Mar. 2026\\
            \subnote{Core member. Project: A broad-spectrum live-attenuated mucosal vaccine against beta-coronaviruses}
      \item \textbf{The HKU-Pasteur Fellowship (4th edition)}, HKU-Pasteur Research Pole \hfill Apr. 2024
      \item \textbf{Faculty Outstanding Research Output Award}, The University of Hong Kong \hfill Feb. 2024\\
            \subnote{awarded twice, for two separate projects}
      \item \textbf{Outstanding Project Team, on COVID-19 research award}, Food and Health Bureau (Hong Kong) \hfill Nov. 2021
      \item \textbf{Postgraduate Scholarship}, The University of Hong Kong \hfill 2016--2020
      \item \textbf{Best Student Poster}, International Symposium for One Health Research (Guangzhou) \hfill 2014
      \item \textbf{Individual Scholarship}, Sun Yat-sen University \hfill 2013
      \item \textbf{The Third Prize Scholarship}, Sun Yat-sen University \hfill 2012
      \item \textbf{First Prize}, Chinese National Olympiad in Biology \hfill Sep. 2010\\
            \subnote{qualified for guaranteed admission to Sun Yat-sen University}
\end{itemize}

\subsection*{GRANTS}
\begin{itemize}
      \item \textbf{General Research Fund (GRF)}, Research Grants Council, Hong Kong SAR \hfill 2026--2027 \\
            \subnote{Early Prediction of SARS-CoV-2 Variant Dynamics: Modelling Virus Interactions with Antibodies and ACE2 Receptor.} \\
            {\small Role: \textbf{Co-I} (PI: Hsiang-Yu Yuan, City University of Hong Kong) \hfill \$840,217 (HKD)}
      \item \textbf{RGC Postdoctoral Fellowship Scheme}, University Grants Committee, Hong Kong SAR \hfill 2023--2026 \\
            \subnote{Quantifying attenuation effects caused by dinucleotide biases and codon pair biases for development of safe and scalable live attenuated virus vaccines.} \\
            {\small Role: \textbf{PI} \hfill \$1,258,250 (HKD)}
      \item \textbf{CEIRR Option (University of Georgia)}, NIH, United States \hfill 2023--2025 \\
            \subnote{Investigation of repeated influenza vaccination for epitope focusing.} \\
            {\small Role: \textbf{Key personnel} (PI: Sophie Valkenburg) \hfill \$454,428 (USD)}
\end{itemize}

\subsection*{TEACHING}
\begin{itemize}
      \item \textbf{Postgraduate Certificate in Bioinformatics for MLT (LMLS6010)}, HKU SPACE \hfill Jan. 2026 \\
            \subnote{Lecturer for 12 classes on Programming for Biological Data}
      \item \textbf{Scientific Skills (LMLS6003)}, MSc in Biomedical Science, HKU SPACE \hfill Oct. 2024 \\
            \subnote{Lecturer for 6 classes on Data Handling in Bioinformatics}
      \item \textbf{Applied Medical Microbiology (LMLS6004)}, MSc in Biomedical Science, HKU SPACE \hfill Nov. 2024 \\
            \subnote{Lecturer for 2 classes on Bioinformatic Tutorial}
\end{itemize}

\subsection*{PUBLICATIONS}
\subsubsection*{Summary}
\begin{center}
      \begin{tabular}{ c c }
            % \hline
            Papers in peer-reviewed journals:       & \textbf{\total{enumi}} (citations: \textbf{\ScholarCitations}; h-index: \textbf{\ScholarHIndex}) \\
            \textit{- first-/last- authored papers} & \textit{\textbf{\total{firstauthorcount}}}                                                       \\
      \end{tabular}
\end{center}

\subsubsection*{Journal papers \textmd{(in reverse chronological order)}:}
\begin{enumerate}
      %% Published
      %% 2026
      \faitem \yr{2026}\myuline{\textbf{Gu, H.}}, Li, J., Sun, W., Li, M., Leung, K., Wu, J. T., Yuan, H.-Y., Wang, M. H., Yang, B., McKay, M. R., Ning, N. \& Poon, L. L. M. \textit{Optimizing global genomic surveillance for early detection of emerging SARS-CoV-2 variants.} \journal{Nature Communications}. (2026)
      \item Song, Z. Y., Zhang, J., Shum, M. H. H., \myuline{\textbf{Gu, H.}}, Shi, W., Siu, G. K. H., Poon, L. L. M., Wu, J. T., Leung, K. S. M. \& Lam, T. T. Y. \textit{Geographical dispersion and transmission of multiple SARS-CoV-2 variants in Hong Kong.} \journal{Urban Informatics}, 5(1), 20. (2026)
      \faitem \myuline{\textbf{Gu, H.}}, Li, M., Wang, R., Lee, L. K., Tam, W. Y., Ho, A. Y. M., Yau, M. C. Y., Yip, K. T., Wong, R. C. W., Wong, B. K. C., Luk, K. S., Lam, J. Y. W., Que, T. L., Chow, V. C. Y., Chau, S. K. Y., Duchene, S., Siu, G. K. H. \& Poon, L. L. M. \textit{Genomic Epidemiology of Hospital-Associated SARS-CoV-2 Clusters in Hong Kong During a Period of Relaxed Visitation (May--August 2022).} \journal{Influenza and Other Respiratory Viruses}, 20(3), e70249. (2026)
      \item Ye, Y., Shuai, H., Song, Y., Shum, M. H.-H., Smith, D. K., \myuline{\textbf{Gu, H.}}, Zhu, H., Wu, J. T., Lewis, N. S., Bonfante, F., Holmes, E. C., Peiris, M., Poon, L. L.-M., Guan, Y. \& Lam, T. T.-Y. \textit{Genomic features associated with sustained mammalian transmission of avian influenza A viruses.} \journal{Nature Microbiology}, s41564-025-02257-4. (2026)
      \item Te, N., Chin, A. W. H., \myuline{\textbf{Gu, H.}}, Jia, J. Z., Huang, Y., Cheng, S. M. S., Tan, C. W., Zhao, J., Hui, K. P. Y., Chan, M. C. W., Feng, B., Quadeer, A. A., McKay, M. R., Wang, L., Valkenburg, S. A., Peiris, M. \& Poon, L. L. M. \textit{Broad beta-CoV immunity and transmission blockade by a single-dose live-attenuated vaccine with atypical codon usage.} \journal{Proceedings of the National Academy of Sciences}, 123(4), e2518645123. (2026)
            %% 2025
      \item \yr{2025}Tuohetasen, S., Qu, Y., Hopke, P. K., Zhang, K., Liu, Y., Lin, S., \myuline{\textbf{Gu, H.}}, Wang, X., Lau, S. S. S., Lin, X., Gao, X., Wu, Y., Zhou, X., Lin, Z., Zhang, M., Sun, Y., Liu, X., Chen, J. \& Zhang, W. \textit{Potential impact of maternal nighttime light exposure and its interaction with sociodemographic characteristics on the risk of various congenital heart diseases.} \journal{Epidemiology}, 36(5), 625--635. (2025)
      \item Zhang, Y., Wei, J., Chen, S., Benmarhnia, T., Zhang, K., Wang, X., Deng, X., \myuline{\textbf{Gu, H.}}, Lin, Z., Qu, Y., Xiao, J., Jiang, J., Du, Z., Zhang, W. \& Hao, Y. \textit{Individual and mixed associations between fine particulate matter components and hospital admissions for hypertension: Insights from a large-scale South Chinese cohort study.} \journal{Sustainable Cities and Society}, 106293. (2025)
      \item Wu, G., Wang, S., Wu, W., Benmarhnia, T., Lin, S., Zhang, K., Xue Romeiko, X., \myuline{\textbf{Gu, H.}}, Qu, Y., Xiao, J., Deng, X., Lin, Z., Du, Z., Zhang, W. \& Hao, Y. \textit{Potential causal links of long-term PM2.5 components exposure with diabetes incidence and mortality in the United States.} \journal{Sustainable Cities and Society}, 106071. (2025)
      \item Sun, W., Choy, K. T., Cheng, K. M., Brackman, C. J., Cheng, S. M. S., Sit, T. H. C., Anne, C. N., Sims, L. D., \myuline{\textbf{Gu, H.}}, Tang, A. W. Y., Wong, A. N. C., Tsang, A. T. L., Koo, J. C. T., Luk, L. L. H., Yen, H.-L., Peris, M. \& Poon, L. L. M. \textit{Detection and characterisation of high pathogenicity avian influenza virus (H5N1/H5N8) clade 2.3. 4.4 b, Hong Kong SAR, China, 2021 to 2024.} \journal{Eurosurveillance}, 2400839. (2025)
      \item Cao, Y., Chin, A. W. H., \myuline{\textbf{Gu, H.}}, Li, M., Gu, Y., Lau, S. P. N., Hui, K. P. Y., Chan, M. C. W. \& Poon, L. L. M. \textit{An interferon-stimulated long non-coding RNA USP30-AS1 as an immune modulator in influenza A virus infection.} \journal{PLOS pathogens}, e1012854. (2025)
            %% 2024
      \item \yr{2024}Wang, X., Zhang, Y., Benmarhnia, T., Zhang, K., Lin, S., Deng, X., \myuline{\textbf{Gu, H.}}, Wu, W., Lin, X., Du, Z., Wang, Y., Qu, Y., Lin, Z., Zhang, M., Sun, Y., Dong, G.-H., Wei, Y., Zhang, W. \& Hao, Y. \textit{The effect of residential greenness on cardiovascular mortality from a large cohort in South China: An in-depth analysis of effect modification by multiple demographic and lifestyle characteristics.} \journal{Environment International}, 108894. (2024)
            \faitem Nelson, C., Poon, L. L. M. \& \myuline{\textbf{Gu, H.}} \textit{Reply to: Population genetic considerations regarding the interpretation of within-patient SARS-CoV-2 polymorphism data.} \journal{Nature Communications}, 15, 3239. (2024)
            \faitem Jia, J.*, Cohen, C.*, \myuline{\textbf{Gu, H.}}*, McLean, M., Varadarajan, R., Bhandari, N., Peiris, M., Leung, G., Poon, L., Chung, A., Cowling, B., Leung, N., Tsang, T. \& Valkenburg, S. \textit{Influenza antibody breadth and effector functions are immune correlates from acquisition of pandemic infection of children.} \journal{Nature Communications}, 15, 3210. (2024)
      \item Cheng, S. M. S., Mok, C. K. P., Li, J. K. C., Chan, K. K. P., Luk, K. S., Lee, B. H. W., \myuline{\textbf{Gu, H.}}, Chan, K. C. K., Tsang, L. C. H., Yiu, K. Y. S., Ling, K. K. C., Tang, Y. S., Luk, L. L. H., Yu, J. K. M., Pekosz, A., Webby, R. J., Cowling, B. J., Hui, D. S. C. \& Peiris, M. \textit{Cross-neutralizing antibody against emerging Omicron subvariants of SARS-CoV-2 in infection-naïve individuals with homologous BNT162b2 or BNT162b2 (WT+ BA. 4/5) bivalent booster vaccination.} \journal{Virology Journal}, 21(1), 1--7. (2024)
            %% 2023
      \item \yr{2023}Xu, X., Deng, Y., Ding, J., Shi, X., Zheng, X., Wang, D., Yang, Y., Liu, L., Wang, C., Li, S., \myuline{\textbf{Gu, H.}}, Poon, L. L. M. \& Zhang, T. \textit{Refining detection methods for emerging SARS-CoV-2 mutants in wastewater: A case study on the Omicron variants.} \journal{Science of The Total Environment}, 904, 166215. (2023)
      \item Xu, X., Deng, Y., Ding, J., Zheng, X., Wang, C., Wang, D., Liu, L., \myuline{\textbf{Gu, H.}}, Peiris, M., Poon, L. L. M. \& Zhang, T. \textit{Wastewater genomic sequencing for SARS-CoV-2 variants surveillance in wastewater-based epidemiology applications.} \journal{Water Research}, 244, 120444. (2023)
      \item Zheng, M. Z. M., Tan, T. K., Villalon-Letelier, F., Lau, H., Deng, Y.-M., Fritzlar, S., Valkenburg, S. A., \myuline{\textbf{Gu, H.}}, Poon, L. L. M., Reading, P. C., Townsend, A. R. \& Wakim, L. M. \textit{Single-cycle influenza virus vaccine generates lung CD8+ Trm that cross react against viral variants and subvert virus escape mutants.} \journal{Science Advances}, 9 (36), eadg3469. (2023)
      \item Xie, R., Edwards, K. M., Adam, D. C., Leung, K. S. M., Tsang, T. K., Gurung, S., Xiong, W., Wei, X., Ng, D. Y. M., Liu, G. Y. Z., Krishnan, P., Chang, L. D. J., Cheng, S. M. S., \myuline{\textbf{Gu, H.}}, Siu, G. K. H., Wu, J. T., Leung, G. M., Peiris, M., Cowling, B. J., Poon, L. L. M. \& Dhanasekaran, V. \textit{Resurgence of Omicron BA.2 in SARS-CoV-2 infection-naive Hong Kong.} \journal{Nature Communications}, 14, 2422. (2023)
            \faitem \myuline{\textbf{Gu, H.}}, Quadeer, A. A., Krishnan, P., Chang, L., Liu, G., Ng, D., Cheng, S., Lam, T., Peiris, M., McKay, M. \& Poon, L. \textit{Within-host genetic diversity of SARS-CoV-2 lineages in unvaccinated and vaccinated individuals.} \journal{Nature Communications}, 14, 1793. (2023)
      \item Adam, D., Martín-Sánchez, M., \myuline{\textbf{Gu, H.}}, Wu, P., Lau, E., Leung, G., Poon, L. \& Cowling, B. \textit{Risk of within-hotel transmission of SARS-CoV-2 during on-arrival quarantine in Hong Kong: an epidemiological and phylogenomic investigation.} \journal{The Lancet Regional Health - Western Pacific}, 100678. (2023)
            %% 2022
      \item \yr{2022}Chu, J. T. S., \myuline{\textbf{Gu, H.}}, Sun, W., Fan, R. L. Y., Nicholls, J. M., Valkenburg, S. A. \& Poon, L. \textit{Heterosubtypic immune pressure accelerates emergence of influenza A virus escape phenotypes in mice.} \journal{Virus Research}, 198991. (2022)
      \item Leong, N., \myuline{\textbf{Gu, H.}}, Ng, Y. M., Chang, L., Krishnan, P., Cheng, S., Peiris, M. \& Poon, L. \textit{Development of multiplex RT-ddPCR assays for detection of SARS-CoV-2 and other common respiratory virus infections.} \journal{Influenza and Other Respiratory Viruses}, 1 (11), 13084. (2022)
      \item Jia, J., Tan, C. W., Cheng, S., \myuline{\textbf{Gu, H.}}, Yeoh, A., Mok, C. K. P., Wang, Y., Zhao, J., Leung, N., Cowling, B., Poon, L., Hui, D., Wang, L.-F., Peiris, M. \& Valkenburg, S. \textit{Priming conditions shape breadth of neutralizing antibody responses to sarbecoviruses.} \journal{Nature Communications}, 13, 6285. (2022)
      \item Hui, K., Ng, K.-C., Ho, J. C. W., Yeung, H.-W., Ching, R. H. H., \myuline{\textbf{Gu, H.}}, Chung, J. C. K., Chow, V. L. Y., Sit, K.-Y., Hsin, M. K. Y., Au, T. W. K., Poon, L., Peiris, J. S., Nicholls, J. \& Chan, M. \textit{Replication of SARS-CoV-2 Omicron BA. 2 Variant in Ex Vivo Cultures of the Human Upper and Lower Respiratory Tract.} \journal{eBioMedicine}, vol. 83: 104232. (2022)
      \item Su, W., Choy, K. T., \myuline{\textbf{Gu, H.}}, Sia, S. F., Cheng, K. M., Nizami, S. I. N., Krishnan, P., Ng, Y. M., Chang, L., Liu, Y., Cheng, S., Peiris, M., Poon, L., Nicholls, J. \& Yen, H.-L. \textit{Reduced Pathogenicity and Transmission Potential of Omicron BA.1 and BA.2 Sublineages Compared with the Early Severe Acute Respiratory Syndrome Coronavirus 2 D614G Variant in Syrian Hamsters.} \journal{Journal of Infectious Diseases}, jiac276. (2022)
      \item Sun, W., Cheng, S., Lam, K., Kwan, T., Wong, R., Lau, L., Liu, G., Luk, L., Li, J., \myuline{\textbf{Gu, H.}}, Peiris, M. \& Poon, L. \textit{Natural Reassortment of Eurasian Avian-Like Swine H1N1 and Avian H9N2 Influenza Viruses in Pigs, China.} \journal{Emerging Infectious Diseases}, 28.7: 1509. (2022)
      \item Bull, M. B., \myuline{\textbf{Gu, H.}}, Ma, F., Perera, L., Poon, L. \& Valkenburg, S. \textit{Next Generation T cell-activating vaccination increases influenza virus mutation prevalence.} \journal{Science Advances}, 8(14), eabl5209. (2022)
      \item Hachim, A., \myuline{\textbf{Gu, H.}}, Kavian, O., Mori, M., Kwan, M., Chan, W. H., Yau, Y. S., Chiu, S., Tsang, O., Hui, D., Mok, C., Ma, F., Lau, E., Amarasinghe, G., Qavi, A., Cheng, S., Poon, L., Peiris, M., Valkenburg, S. \& Kavian, N. \textit{SARS-CoV-2 accessory proteins reveal distinct serological signatures in children.} \journal{Nature Communications}, 13: 2951. (2022)
      \item Yen, H.-L., Sit, T., Brackman, C., Chuk, S., \myuline{\textbf{Gu, H.}}, Tam, K., Law, P., Leung, G., Peiris, M., Poon, L., Cheng, S., Chang, L., Krishnan, P., Ng, D., Liu, G., Hui, M., Ho, S. Y., Su, W., Sia, S. F., Choy, K.-T., Cheuk, S., Lau, S., Tang, A., Koo, J. \& Yung, L. \textit{Transmission of SARS-CoV-2 delta variant (AY. 127) from pet hamsters to humans, leading to onward human-to-human transmission: a case study.} \journal{The Lancet}, 399.10329: 1070--1078. (2022)
            \faitem \myuline{\textbf{Gu, H.}}*, Xie, R.*, Adam, D.*, Tsui, J.*, Chu, D.*, Chang, L., Cheuk, S., Gurung, S., Krishnan, P., Ng, D., Liu, G., Wan, C., Cheng, S., Edwards, K., Leung, K., Wu, J., Tsang, D., Leung, G., Cowling, B., Peiris, M., Lam, T., Dhanasekaran, V. \& Poon, L. \textit{Genomic epidemiology of SARS-CoV-2 under an elimination strategy in Hong Kong.} \journal{Nature Communications}, 13, 736 : 1--10. (2022)
      \item Hui, K., Ho, J., Cheung, M.-C., Ng, K.-C., Ching, R., Lai, K.-L., Kam, T., \myuline{\textbf{Gu, H.}}, Sit, K.-Y., Hsin, M., Au, T., Poon, L., Peiris, M., Nicholls, J. \& Chan, M. \textit{SARS-CoV-2 Omicron variant replication in human respiratory tract ex vivo.} \journal{Nature}, 603: 715--720. (2022)
            \faitem \myuline{\textbf{Gu, H.}}, Ng, D., Liu, G., Cheng, S., Krishnan, P., Chang, L., Cheuk, S., Hui, M., Lam, T., Peiris, M. \& Poon, L. \textit{Recombinant BA. 1/BA. 2 SARS-CoV-2 Virus in Arriving Travelers, Hong Kong, February 2022.} \journal{Emerging infectious diseases}, 28 (6) : 1276. (2022)
            \faitem \myuline{\textbf{Gu, H.}}, Krishnan, P., Ng, D., Chang, L., Liu, G., Cheng, S., Hui, M., Fan, M., Wan, J., Lau, L., Cowling, B., Peiris, M. \& Poon, L. \textit{Probable Transmission of SARS-CoV-2 Omicron Variant in Quarantine Hotel, Hong Kong, China, November 2021.} \journal{Emerging infectious diseases}, 28 (2): 460. (2022)
            \faitem \myuline{\textbf{Gu, H.}}, Cheng, S., Krishnan, P., Ng, D., Chang, L., Liu, G., Cheuk, S., Hui, M., Fan, M., Wan, J., Lau, L., Chu, D., Dhanasekaran, V., Peiris, M. \& Poon, L. \textit{Monitoring International Travelers Arriving in Hong Kong for Genomic Surveillance of SARS-CoV-2.} \journal{Emerging infectious diseases}, 28(1): 247--250. (2022)
            %% 2021
            \faitem \yr{2021}\myuline{\textbf{Gu, H.}}, Chu, D., Chang, L., Cheuk, S., Gurung, S., Krishnan, P., Ng, D., Liu, G., Wan, C., Xie, R., Cheng, S., Cowling, B., Tsang, D., Peiris, M., Dhanasekaran, V. \& Poon, L. \textit{Genetic Diversity of SARS-CoV-2 among Travelers Arriving in Hong Kong.} \journal{Emerging infectious diseases}, 27(10): 2666--2668. (2021)
      \item Dhanasekaran, V., Edwards, K., Xie, R., \myuline{\textbf{Gu, H.}}, Adam, D. C., Chang, L., Cheuk, S., Gurung, S., Krishnan, P., Ng, D., Liu, G., Wan, C., Cheng, S., Tsang, D., Cowling, B., Peiris, M. \& Poon, L. \textit{Air travel-related outbreak of multiple SARS-CoV-2 variants.} \journal{Journal of Travel Medicine}, taab149. (2021)
            \faitem Chu, D.*, \myuline{\textbf{Gu, H.}}*, Chang, L., Cheuk, S., Gurung, S., Krishnan, P., Ng, D., Liu, G., Wan, C., Tsang, D., Peiris, M. \& Poon, L. \textit{SARS-CoV-2 superspread in fitness center, Hong Kong, China, March 2021.} \journal{Emerging infectious diseases}, 27(8): 2230--2232. (2021)
      \item Chu, D.*, Hui, K.*, \myuline{\textbf{Gu, H.}}, Ko, R. L. W., Krishnan, P., Ng, D., Liu, G., Wan, C., Cheung, M.-C., Ng, K.-C., Nicholls, J., Tsang, D., Peiris, M., Chan, M. \& Poon, L. \textit{Introduction of ORF3a-Q57H SARS-CoV-2 variant causing fourth epidemic wave of COVID-19, Hong Kong, China.} \journal{Emerging infectious diseases}, 27(5): 1492--1495. (2021)
            %% 2020
            \faitem \yr{2020}\myuline{\textbf{Gu, H.}}, Chu, D., Peiris, M. \& Poon, L. \textit{Multivariate analyses of codon usage of SARS-CoV-2 and other betacoronaviruses.} \journal{Virus Evolution} 6, no. 1: veaa032. (2020)
      \item Sah, R., Rodriguez-Morales, A. J., Jha, R., Chu, D., \myuline{\textbf{Gu, H.}}, Peiris, M., Bastola, A., Lal, B. K., Ojha, H. C., Rabaan, A. A., Zambrano, L. I., Costello, A., Morita, K., Pandey, B. D. \& Poon, L. \textit{Complete genome sequence of a 2019 novel coronavirus (SARS-CoV-2) strain isolated in Nepal.} \journal{Microbiology Resource Announcements} 9, no. 11. (2020)
            \faitem \yr{2019}\myuline{\textbf{Gu, H.}}, Fan, R., Wang, D. \& Poon, L. \textit{Dinucleotide evolutionary dynamics in influenza A virus.} \journal{Virus Evolution} 5, no. 2: vez038. (2019)
      \item \yr{2018}Hussain, A.-G., Chu, D., Rihan, E. M. A., Abd-Allah, E. M., \myuline{\textbf{Gu, H.}}, Chin, A., Qasim, I. A., Aldoweriej, A., Alharbi, S. S., Al-Aqil, M. A., Al-Sahaf, A., Abdel Rahman, S. S., Aljassem, A. H., Abdul-Al, A., Aljasir, M. R., Alhammad, Y. M. O., Kasem, S., Peiris, M., Zaki, A. Z. S. A. \& Poon, L. \textit{Circulation of Influenza A (H5N8) Virus, Saudi Arabia.} \journal{Emerging Infectious Diseases} 24, no. 10: 1961. (2018)
            \faitem \yr{2016}\myuline{\textbf{Gu, H.}}, Leung, R. K.-K., Jing, Q., Zhang, W., Yang, Z., Lu, J., Hao, Y. \& Zhang, D. \textit{Meteorological Factors for Precise Dengue Fever Control and Prevention in South China.} \journal{International Journal of Environmental Research and Public Health}, 13(9), 867. (2016)
            \faitem Chen, T.*, \myuline{\textbf{Gu, H.}}*, Leung, R. K.-K., Liu, R., Chen, Q., Wu, Y. \& Li, Y. \textit{Evidence-Based interventions of Norovirus outbreaks in China.} \journal{BMC Public Health}, 16(1): 1072. (2016)
            \faitem \yr{2015}\myuline{\textbf{Gu, H.}}, Zhang, W., Xu, H., Li, P., Wu, L., Guo, P., Hao, Y., Lu, J. \& Zhang, D. \textit{Predicating risk area of human infection with avian influenza a (H7N9) virus by using early warning model in China.} \journal{Chinese Journal of Epidemiology}, 36(5): 470--475. (2015)
      \item \yr{2014}Li, P., Xu, H., \myuline{\textbf{Gu, H.}}, Ma, M., Lu, J., Hao, Y. \& Zhang, D. \textit{Epidemiological Characteristics of Influenza Virus H7N9 and Evolutionary Analysis of Hemagglutinin and Neuraminidase Genes.} \journal{Journal of Sun Yat-sen University (Medical Sciences)}, 06. (2014)
\end{enumerate}

%% ============================================================================
%% PLACEHOLDER (commented out) -- reserved research-output slot for the
%% "Built with Claude: Life Sciences" hackathon finding (Research track, Jul 2026).
%% TO ACTIVATE: fill the <...> fields and delete the leading "% " on each line below.
%% Notes: a Zenodo DOI on the GitHub write-up (or a bioRxiv/medRxiv preprint) makes
%%   this citable. Uses itemize (NOT enumerate) on purpose so it does not inflate the
%%   \total{enumi} journal-paper count shown in the Summary above.
%% ============================================================================
% \subsubsection*{Preprints \textmd{and working papers}:}
% \begin{itemize}
%       \item <Author 1>, ..., \myuline{\textbf{Haogao Gu}}, ..., <Last Author>. \textit{<Title>.} \journal{<bioRxiv / medRxiv / Zenodo>}, <DOI or ID>. (2026) \\
%             \subnote{Produced at Built with Claude: Life Sciences (Anthropic $\times$ Gladstone Institutes), Research track; selected 1 of 500 from 6,000+ applicants.}
% \end{itemize}

\subsection*{SUPERVISION}
\subsubsection*{Co-supervision:}
\begin{itemize}
      \item Ruixuan Wang, PhD student, The University of Hong Kong \hfill Feb. 2025 -- May 2026 \\ \subnote{Within-host Viral Phylodynamics}
      \item Mengting Li, PhD student, The University of Hong Kong \hfill Oct. 2025 -- May 2026 \\ \subnote{Virtual Cell and Viral Infection}
\end{itemize}

\subsection*{INVITED TALKS}
\begin{itemize}
      \item \textbf{Genomic Surveillance and Molecular Epidemiology of SARS-CoV-2 in Hong Kong}.  \hfill Jul. 2025 \\ \small \textit{XLII Annual Meeting of the Willi Hennig Society,
                  The Chinese University of Hong Kong, HKSAR, China}
\end{itemize}

\subsection*{PROFESSIONAL DEVELOPMENT}
\subsubsection*{Workshops:}
\begin{itemize}
      \item \textit{Workshop on Molecular Evolution}, Marine Biological Laboratory (MBL), Woods Hole, MA, USA \hfill May 2025
      \item \textit{Virus Evolution and Epidemiology Summer Course}, Croucher Foundation, Hong Kong \hfill Jul. 2024
      \item \textit{Models and Inference in Population Genetics IV}, University of Warwick, UK \hfill Apr. 2024
\end{itemize}
\subsubsection*{Online specializations:}
\begin{itemize}
      \item \textit{Discrete Mathematics for Computer Science}, University of California San Diego \hfill Oct. 2019
      \item \textit{Bayesian Statistics and Modelling}, University of California Santa Cruz \hfill Aug. 2019
      \item \textit{Python 3 Programming}, University of Michigan \hfill Jun. 2019
      \item \textit{Mathematics for Machine Learning}, Imperial College London \hfill Apr. 2019
\end{itemize}
\subsubsection*{Teaching aptitude:}
\begin{itemize}
      \item Certificate of Teaching and Learning in Higher Education, CETL, HKU \hfill Dec. 2024
      \item PBL Tutor Training Certificate, LKS Faculty of Medicine, The University of Hong Kong \hfill Oct. 2025
\end{itemize}

\subsection*{ACADEMIC SERVICES}
\subsubsection*{Managing editor:}
\journal{Virology Journal}

% \subsubsection*{Review for journals:}
% \begin{multicols}{2}
% \begin{itemize}
%   \item \textsc{Emerging Infectious Diseases}
%   \item \textsc{Communications Medicine}
%   \item \textsc{PLOS Pathogens}
%   \item \textsc{Virus Evolution}
%   \item \textsc{npj Viruses}
%   \item \textsc{Virology Journal}
%   \item \textsc{Infection, Genetics and Evolution}
%   \item \textsc{Epidemics}
%   \item \textsc{Influenza and Other Respiratory Viruses}
%   \item \textsc{Cellular and Molecular Life Sciences}
%   \item \textsc{Scientific Reports}
%   \item \textsc{Frontiers in Immunology}
%   \item \textsc{BMC Microbiology}
%   \item \textsc{BMC Medical Research Methodology}
%   \item \textsc{Journal of Multidisciplinary Healthcare}
% \end{itemize}
% \end{multicols}

\subsubsection*{Ad hoc peer reviewer:}
{\small
\begin{tabularx}{\linewidth}{Y Y}
      \textsc{Science}                                 & \textsc{The Lancet Microbe}                      \\
      \textsc{Communications Medicine}                 & \textsc{Emerging Infectious Diseases}            \\
      \textsc{PLOS Pathogens}                          & \textsc{Cellular and Molecular Life Sciences}    \\
      \textsc{Frontiers in Immunology}                 & \textsc{Influenza and Other Respiratory Viruses} \\
      \textsc{Virus Evolution}                         & \textsc{Scientific Reports}                      \\
      \textsc{npj Viruses}                             & \textsc{Epidemics}                               \\
      \textsc{Virology Journal}                        & \textsc{BMC Microbiology}                        \\
      \textsc{BMC Medical Research Methodology}        & \textsc{Infection, Genetics and Evolution}       \\
      \textsc{Journal of Multidisciplinary Healthcare} &                                                  \\
\end{tabularx}
}

\subsubsection*{Open-source software:}
\begin{itemize}
      \item \textbf{Author}, \href{https://doi.org/10.18129/B9.bioc.SynMut}{\texttt{SynMut}}, \subnote{Synonymously Mutated Sequences with Different Genomic Signatures}
      \item \textbf{Author}, \href{https://github.com/Leo-Poon-Lab/GEII}{\texttt{GEII}}, \subnote{Host Gene Expression under Influenza virus infection or Interferon stimulation}
      \item \textbf{Author}, \href{https://github.com/Koohoko/epitope_diversity}{\texttt{epitope\_diversity}}, \subnote{Estimating epitope diversity at haplotype level using NGS reads}
      \item \textbf{Author}, \href{https://github.com/Koohoko/fasta_filter}{\texttt{fasta\_filter}}, \subnote{Filtering fasta sequences with threshold of specific bases}
      \item \textbf{Contributor}, \href{https://github.com/spatPomp-org/spatPomp}{\texttt{spatPomp}}, \subnote{Inference for Spatiotemporal Partially Observed Markov Processes}
      \item \textbf{Contributor}, \href{https://github.com/Rdatatable/data.table}{\texttt{data.table}} (Chinese translation), \subnote{High-performance R package}
\end{itemize}

\subsubsection*{Professional leadership:}
\begin{itemize}
      \item Founder and sole lecturer of a weekly reading group on Molecular Evolution. \hfill Feb. 2025 -- Dec. 2025 \\ \small \textit{Personally delivered every session, teaching Ziheng Yang's ``Molecular Evolution: The Statistical Approach'' to 20 researchers from different regions and disciplines} \normalsize
      \item Generating and drafting weekly reports to Hong Kong public health authorities. \hfill 2020 -- 2022 \\ \small \textit{On SARS-CoV-2 genomic epidemiology for timely pandemic responses} \normalsize

\end{itemize}


\vfill {\footnotesize\itshape CV updated: \CVDate{} \textbullet{} Citation metrics updated: \ScholarUpdated}
\end{document}
